Synthesizing Quotient Lenses

### 2018-07-07 papers/QuotientLenses/main.tex

In summary, our main contributions are:
\begin{enumerate}
  \item We introduce {\em Quotient Regular Expressions} (QREs), 
  a compact, convenient notation for simultaneously defining a
  regular language modulo some equivalence relation and a canonizer
  for that relation (Section~\ref{QRE}).
  \item We introduce {\em QRE lenses}, which translate between data formats
  specified using QREs (Section~\ref{QRE-lenses}).
  \item We design a specific set of useful QRE lens combinators and prove
  that QRE lenses defined using these combinators can be put into a
  restricted normal form (Section~\ref{QRE-lenses}).  This is
  the main technical contribution of this paper.
  \item We leverage this result to reduce the problem of {\em synthesizing}
  QRE lenses to the problem of synthesizing bijective string lenses, which was
  previously studied in past work~\cite{optician} (Section~\ref{synth}).
  \item We extend Boomerang with QREs and QRE lens synthesis and demonstrate
  the utility and practicality of our approach by synthesizing QRE lenses
  between a variety of data formats drawn from the Optician benchmark suite
  (Section~\ref{impl}).
\end{enumerate}
Sections~\ref{relwork} and~\ref{concl} present related and future work.

@@

>>>>

In summary, our main contributions are:
\begin{enumerate}
  \item We introduce {\em Quotient Regular Expressions} (QREs), 
  a compact, convenient notation for simultaneously defining a
  regular language modulo some equivalence relation and a canonizer
  for that relation (Section~\ref{QRE}).
  \item We introduce {\em QRE lenses}, which translate between data formats
  specified using QREs (Section~\ref{QRE-lenses}).
  \item We design a specific set of useful QRE lens combinators and prove
  that QRE lenses defined using these combinators can be put into a
  restricted normal form (Section~\ref{QRE-lenses}).  This is
  the main technical contribution of this paper.
  \item We leverage this result to reduce the problem of {\em synthesizing}
  QRE lenses to the problem of synthesizing bijective string lenses, which was
  previously studied in past work~\cite{miltner2017synthesizing} (Section~\ref{synth}).
  \item We extend Boomerang with QREs and QRE lens synthesis and demonstrate
  the utility and practicality of our approach by synthesizing QRE lenses
  between a variety of data formats drawn from the Optician benchmark suite
  (Section~\ref{impl}).
\end{enumerate}
Sections~\ref{relwork} and~\ref{concl} present related and future work.

@@

\begin{acks}
  We thank our anonymous reviewers for their useful feedback and discussions and Nate Foster for his extensive assistance in integrating
  QRE-enhanced \QOpt{} into Boomerang.  This research has been supported in part by DARPA
  award FA8750-17-2-0028 and ONR 568751 (SynCrypt).
\end{acks}
